

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
\exhyphenpenalty=10000

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {WEX Health} % Organization
    {Software Development Engineer} % Job title
    {} % Location
    {Jul. 2023 - Aug. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Engineered advanced iOS applications using Swift and Objective-C, elevating user engagement through optimized MVC and MVVM designs to drive a 15\% increase in usage.}
    \item {Enhanced CI/CD pipeline efficiency by 35\% through improved unit test coverage, diminishing critical errors and stabilizing product releases.}
    \item {Automated development workflows utilizing Microsoft Azure and Jenkins, significantly reducing task complexity and fostering enhanced collaboration within the team.}
    \item {Partnered with cross-functional teams to refine back-end integrations, resulting in superior app performance and security enhancements for client data.}
      \end{cvitems}
    }

  \cventry
    {WEX Health} % Organization
    {Software Engineer Intern} % Job title
    {} % Location
    {Sep. 2022 - Jul. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a scalable test automation suite using Python and Selenium, achieving a 30\% reduction in manual testing efforts while ensuring high software quality.}
    \item {Authored C\# test scripts for identifying critical API performance issues, bolstering the WEX Partner Benefit Analytics portal's reliability and user experience.}
    \item {Automated extensive database validations ensuring 99\% accuracy in SQL stored procedures, directly enhancing overall data integrity of applications.}
    \item {Participated in Agile/SCRUM methodologies, contributing to rapid prototyping and iterative releases, vital for delivering high-quality software solutions.}
      \end{cvitems}
    }

  \cventry
    {United States Army} % Organization
    {Base Expeditionary Targeting and Surveillance Systems Operator and Team Leader} % Job title
    {} % Location
    {Apr. 2014 - Apr. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led teams in managing advanced surveillance systems while deployed, integrating ISR technologies to enhance operational effectiveness in high-pressure environments.}
    \item {Automated real-time data collection and analysis processes for surveillance systems, providing strategic insights that improved mission success rates.}
    \item {Instrumental in implementing geospatial intelligence methodologies, increasing situational awareness and operational coordination across diverse teams.}
    \item {Awarded the Army Achievement Medal for exceptional leadership and unwavering commitment to operational excellence during critical missions in diverse environments.}
      \end{cvitems}
    }
\end{cventries}
