%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
\exhyphenpenalty=10000

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

        \cventry
          {Individual Developer} % Role
          {Resume Optimization and Compilation Tool} % Event
          {} % Location
          {In active development} % Date(s)
          {
            \begin{cvitems} % Description(s)
            \item {Developed a resume optimization tool using Node.js to tailor content for specific job applications, enhancing ATS compatibility.}
    \item {Leveraged OpenAI's API for analyzing job descriptions and transforming existing resumes for better marketability.}
    \item {Implemented LaTeX for professional PDF output, ensuring clean formatting for resume submissions, boosting employer engagement.}
            \end{cvitems}
          }

        \cventry
          {Individual Developer} % Role
          {IoT-Based Smart Energy Management Tool} % Event
          {} % Location
          {In active development} % Date(s)
          {
            \begin{cvitems} % Description(s)
            \item {Engineered a real-time energy monitoring system utilizing Node.js and Python, enhancing energy efficiency for smart environments.}
    \item {Automated HVAC optimization through intelligent controls, decreasing utility costs significantly.}
    \item {Employed data analysis techniques for energy loss identification, highlighting capabilities in data management and system performance improvement.}
            \end{cvitems}
          }

        \cventry
          {Individual Developer} % Role
          {QuackieChattie (Android and iOS)} % Event
          {} % Location
          {2022-2023} % Date(s)
          {
            \begin{cvitems} % Description(s)
            \item {Designed and developed a multi-user chat application for Android/iOS, integrating Node.js for backend support and data management.}
    \item {Implemented Firebase and Google Sign-In for secure user authentication and efficient authorization management.}
    \item {Deployed a Heroku PostgreSQL database, showcasing experience with cloud services and database management.}
            \end{cvitems}
          }

        \cventry
          {Microservices Developer} % Role
          {DNYF: Study Buddies} % Event
          {} % Location
          {2022} % Date(s)
          {
            \begin{cvitems} % Description(s)
            \item {Collaboratively developed a group study web application on AWS, demonstrating skills in distributed systems and microservices architecture.}
    \item {Applied REST APIs with Node.js and Express.js to ensure efficient communication between services, optimizing application responsiveness.}
    \item {Utilized Docker for microservices deployment on AWS, aligning with Cloudflare's use of modern deployment technologies.}
            \end{cvitems}
          }
\end{cventries}
